What's in a Name? \\ Linear Temporal Logic \\ Literally Represents Time Lines

### 2023-08-29 paper/main.tex
rewording

%\paragraph{Scalability}
{\bf Scalability.}
%KYR: FIX!!! The description of the exact experiment run is not clear and seems to contradict the points in the above paragraph...
We measure the scalability of our tool by running it against a set of \emph{scalable} LTL formulas. We define a scalable LTL formula as one that describes an $n$-bit number using a binary counter, as generated by~\cite{RV10}. As $n$ gets larger, the LTL formula required to encode the $n$-bit counter scales in size. \cref{fig:scalability} shows that the timeline length grows approximately exponentially with the number of bits in the counter, which matches the result in Rozier and Vardi~\cite{RV10}. The set of formulas being tested can be found \href{https://github.com/EULIR/ltl-explainability/tree/main/ltl-formulas/binary_counter}{here}.

@@

%KYR: FIX: is timeout 20 seconds or 30 seconds?!?!? It still sounds like this is the same test as the paragraph above but with a different timeout. Please describe the difference in the tests; what was run exactly for a 30 second timeout and why was this different than the 20 second timout?

>>>>

%\paragraph{Scalability}
{\bf Scalability.}
We study the scalability of our tool on a benchmark suite of LTL formulas that scales in size. According to Rozier and Vardi~\cite{RV10}, the LTL formula required to encode a $n$-bit binary counter scales in size as $n$ gets larger. Therefore the benchmark for scalability consists of LTL formulas that describe $n$-bit counters. \cref{fig:scalability} shows that the timeline length grows approximately exponentially with the number of bits in the counter, which matches the result in Rozier and Vardi~\cite{RV10}. The set of formulas being tested can be found \href{https://github.com/EULIR/ltl-explainability/tree/main/ltl-formulas/binary_counter}{here}.

@@
